---
title: "R Notebook"
output: html_notebook
---

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 



```{r}
#importing libraries
library(utils)
library(base)

library(dplyr)
library(ggplot2)
library(graphics)
library(caTools)
library(Metrics)
library(lubridate)
library(stringr)
library(caret)



#importing dataset
df <- read.csv('https://raw.githubusercontent.com/anthoniraj/dsr_datasets_final/main/19BDS0153.csv')
#df
df1 <- df
#View(df1)
```


```{r}
#preprocesing
df1$Datetimes <- as.POSIXct(df1$Datetime)

df1$Date <- as.Date(ymd_hms(df1$Datetime))

head(df1)
#View(df1)
```


```{r}
#splitting the dataset using 80:20 rule

df1$split = sample.split(df1$Adj.Close, SplitRatio=0.8)
head(df)

train = subset(df1, df1$split == TRUE)
test = subset(df1, df1$split == FALSE)
head(df1)
head(test)
head(train)

# Build the model on training data
lmMod1 <- lm(Close ~ Low + High, data=train)  # build the model

Predicted <- predict(lmMod1, test)  # predict scores

summary(lmMod1)

#comparing actual vs predicted
#actuals_preds <- data.frame(cbind(Volume=test$Volume, Actual_High=test$High, Actual_Low=test$Low, Predicted_Price=Predicted))  

# make predicted dataframe with test set
df2 <- test
df2$Predicted_price <- Predicted

head(df2)
```

```{r}

#Calculating MSE, MAE RMSE and R squared manually
Original = df2$Adj.Close
d = Original - Predicted
mse = mean((d)^2)
mae = mean(abs(d))
rmse = sqrt(mse)
R2 = 1-(sum((d)^2)/sum((Original-mean(Original))^2))
cat(" MAE:", mae, "\n", "MSE:", mse, "\n", 
     "RMSE:", rmse, "\n", "R-squared:", R2)

#Calculating MSE, MAE RMSE and R squared with functions
  
MAE(Predicted, Original)
mse(Predicted, Original)
 
RMSE(Predicted, Original)
R2(Predicted, Original, form = "traditional")
 
```

```{r}
#plotting the predicted value and actual values

library(ggplot2)

ggplot(df2, aes(x = Date)) +
  geom_line(aes(y = Adj.Close, color = "Actual Close")) + ggtitle("Closing Stock Price: ASHOKLEY") +
  geom_line(aes(y = Predicted_price, color = "Predicted Close")) +
  geom_line(aes(y = Open, color = "Open")) + xlab("Date ") + ylab("Stock Price") +
  theme(plot.title = element_text(hjust = 0.5), panel.border = element_blank()) +
  scale_x_date(date_breaks = "3 days") +
  scale_colour_manual("Series", values=c("Actual Close"="gray40", "Predicted Close"="firebrick4", "Open"="darkcyan"))

plot(Predicted)

plot(df2)

###ggplot(df2,aes(Date,Adj.Close)) + 
#  geom_line(aes(color="Original")) +
#  geom_line(df2=Predicted,aes(color="Predicted")) +
#  labs(color="Legend") +
#  scale_colour_manual("", breaks = c("Original", "Predicted"),
#                          values = c("blue", "brown")) +
#  ggtitle("Closing Stock Prices") + 
#  scale_x_date(date_breaks = "2 days") +
#  theme(plot.title = element_text(lineheight=.7, face="bold"))
```


```{r}
df2 = subset(df2, select = -c(split, Datetimes, Datetime) )
#rm(df2)
```



